\section{Design Details for Evolution Scenarios}
In this chapter we provide the detailed design documentation for each of the evolution scenarios
introduced in the prior section. Sec. \ref{App} sketches the design decision for the Mobile App that provides a second sales channel next to the existing Pick-up Shop. Sec. \ref{Docker} describes the adaptive evolution scenario of setting up a Docker environment to simplify the update process. They are both based on, or at least use the Hybrid Cloud-based Variant of CoCoME \cite{SWB-469002735}. In contrast, Sec. \ref{MS} provides a detailed design documentation of a new architectural version of CoCoME. This perfective evolution scenario is realized based on the Microservice idea.

\subsection{Design Decisions for the Mobile App} \label{App}
	%TODO Add most important information od App-Paper


\subsection{Setting up a Docker environment} \label{Docker}
	%TODO Add most important information of docker paper
	
	
\subsection{Using Microservices Technology} \label{MS}
	\begin{itemize}
		\item je microservice absatz mit entsprechenden Sequenzendiagram %fertig machen der implementierung
		\item frontend? muss dazu auch das gemacht werden?
		\item ein blocktext zu mehereren diagrammen oder diagramme zwischen text?
		
	
			\item je die einzelnen module und szenarien erlaeutern in dem diese sinnvoll sind
	\end{itemize}
	
		\subsubsection{Products}
		abstrahieren der Produktinformationen 
		
		\subsubsection{Stores}
		einzelne Laeden alleinstehend abbilden um nach bedarf neue microservices alias laeden starten zu können
		
		\subsubsection{Enterprise}
		aehnlich zu stroes
		
		\subsubsection{Reports}
		stellt alleinigen aufgaben bereich dar, entsprechen undabhaengig darzustellen von anderem.




	
	
(grafik/Tabelle  -> oben oder unten caption)